%!TEX TS-program = xelatex

% compile with:
% xelatex cv
% biber cv
% xelatex cv
% xelatex cv

\documentclass[print]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{jelmer}{tiete}
       {electronics engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    610W 115th apt94
    10025 New York City
    USA
    ~
    \href{mailto:jelmer@tiete.be}{\textcolor{textcolor}{\faEnvelopeAlt}~jelmer@tiete.be}
    \href{http://jelmertiete.com}{\textcolor{textcolor}{\faGlobe}~jelmertiete.com}
    \href{http://twitter.com/jelmt}{\textcolor{textcolor}{\faTwitter}~@jelmt}
    \href{https://github.com/JelmerT}{\textcolor{textcolor}{\faGithub}~JelmerT}
  \section{languages}
    dutch
    english
    french
    german (notions)
  \section{programming}
    % {\color{red} $\varheartsuit$} JavaScript
    Python, C, ASM
    HTML, PHP, CSS
    JavaScript, node.js
    Matlab, Latex
    Verilog, VHDL
  \section{platforms}
    6LoWPAN, BLE
    CC25XX, MSP430
    mbed, Arduino
    Beaglebone, rPi
    3D printing
  \section{software}
    Contiki, TinyOS
    Altium, Eagle
    Autocad, IAR
\end{aside}

\section{interests}
I'm a maker at heart and have a strong background in wireless sensor networks and computer science. My interests go out to electronic hardware design, research and (rapid) prototyping. I'm looking for more experience in supply chain logistics for consumer products. In all I'm a solution driven person, eager to learn and feel comfortable in a fast changing environment.

\section{education}

\begin{entrylist}
  \entry
    {since 2010}
    {Ph.D. {\normalfont candidate in the engineering sciences}}
    {VUB, Vrije Universiteit Brussel}
    {\emph{Monitoring Noise Pollution with Microphone Array-Based Wireless Sensor Networks} - Expected begin 2015}
  \entry
    {2008–2010}
    {M.Sc. {\normalfont industrial engineering - distinction}}
    {EhB, Erasmus Hogeschool Brussel}
    {Majoring in electronics - ICT\\
    \emph{Wireless link estimation in Contiki based sensor networks} in collaboration with Hanoi University of Technology - Vietnam}
  \entry
    {2004–2008}
    {B.Sc. {\normalfont industrial engineering - distinction}}
    {EhB, Erasmus Hogeschool Brussel}
    {Majoring in electronics - ICT}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2014}
    {\href{http://beyond.io}{beyond.io, Antwerp, Belgium}}
    {R\&D Engineer}
    {\emph{PCB design, firmware development and production consulting for diverse prototypes.}}
  \entry
    {1-12 2011}
    {Zaffer BVBA, Zaventem, Belgium}
    {R\&D Engineering internship}
    {\emph{Development and production start-up of a wireless window-shutter control system, including electronic design of several remote controls and motors. Development of firmware and software for smart remote controls and their wireless network.}}
  \entry
    {2010 - 2014}
    {FabLaBXL, Brussels, Belgium}
    {Fab lab manager}
    {\emph{Start up and daily operations of an open workshop for students, artists and engineers where digital fabrication tools can be used freely to produce small scale products or projects.}}
  \entry
    {2007 - 2012}
    {Culture Club, Ghent, Belgium}
    {Light technician}
    {\emph{Head technician, light director during events and evenings. Technical maintenance of light- sound and video-material. Technical advisor for events.}}
  \entry
    {07 2007}
    {Right Management Consultants, Brussels, Belgium}
    {IT Consultant summer job}
    {\emph{Revising and adjusting company intranet site and accompanying databases.}}
  \entry
    {07-08 2004/5}
    {Thomson (Grass Valley), Brussels, Belgium}
    {Audio-visual technician summer job}
    {\emph{Assistance in the deployment of diverse audio-visual installations in radio and TV studios (European commission, Flemish Parliament, ...).}}
  \entry
    {2004 - 2014}
    {Freelance, Europe}
    {Light-, sound- and video technician}
    {\emph{Providing a full technical framework for events, shows, parties, performances, conferences, theater and live events. Designing of light-, sound-, video-, and power-plans. Programming and operating of diverse lighting- and video desks. 
    %Construction of full lighting rigs.
    }}
\end{entrylist}

\section{publications}


\printbibsection{article}{article in peer-reviewed journal}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
\end{refsection}
\begin{refsection}
  \nocite{*}
  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
\end{refsection}
\printbibsection{misc}{other publications}
\printbibsection{report}{research reports}

\end{document}
