%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% K-CV -- Klenske Curriculum Vitae
% 
% Simplified Friggeri CV 
% by Edgar Klenske (ed.klenske@gmx.de)
% https://github.com/eklenske/CV
%
% Forked from:
% Jelmer Tiente 
% https://github.com/JelmerT/CV
%
% Based on original work by:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{k-cv} % Add 'print' as an option into the square
                       % bracket to remove colors from this template
                       % for printing


\begin{document}
\header{john}{smith}{junior business analyst} % Your name and current job

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{date of birth}
\color{gray}1970-01-01
\section{contact}
123 Broadway
City, State 12345
Country
~
+0 (000) 111 1111
+0 (000) 111 1112
~
\href{mailto:john@smith.com}{john@smith.com}
\href{http://www.smith.com}{http://www.smith.com}
\href{http://facebook.com/johnsmith}{fb://jsmith}
\section{languages}
english mother tongue
spanish \& italian fluency
\section{programming}
JavaScript
Python, C++, PHP
CSS3 \& HTML5
\end{aside}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011 \to 2012}
{Master {\normalfont of Commerce}}
{The University of California, Berkeley}
{\emph{Money Is The Root Of All Evil -- Or Is It?} \\ This thesis explored the 
idea that money has been the cause of untold anguish and suffering in the world. 
I found that it has, in fact, not.}
%------------------------------------------------
\entry
{2007 \to 2008}
{Bachelor {\normalfont of Business Studies}}
{The University of California, Berkeley}
{Specialization in Commerce}
%------------------------------------------------
\end{entrylist}

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2012 \to now}
{LEHMAN BROTHERS}
{Los Angeles, California}
{\emph{1\textsuperscript{st} Year Analyst} \\
Developed spreadsheets for risk analysis on exotic derivatives on a wide array 
of commodities (ags, oils, precious and base metals), managed blotter and 
secondary trades on structured notes, liaised with Middle Office, Sales and 
Structuring for bookkeeping. \\
Detailed achievements:
\begin{itemize}
\item Learned how to make amazing coffee
\item Finally determined the reason for \textsc{PC LOAD LETTER}:
\begin{itemize}
\item Paper jam
\item Software issues:
\begin{itemize}
\item Word not sending the correct data to printer
\item Windows trying to print in letter format
\end{itemize}
\item Coffee spilled inside printer
\end{itemize}
\item Broke the office record for number of kitten pictures in cubicle
\end{itemize}}
%------------------------------------------------
\entry
{2010 \to 2011}
{LEHMAN BROTHERS}
{London, United Kingdom}
{\emph{Summer Intern} \\
Rated "truly distinctive" for Analytical Skills and Teamwork.}
%------------------------------------------------
\entry
{2008 \to 2009}
{Buy More}
{Burbank, California}
{\emph{Computer Repair Specialist} \\
Worked in the Nerd Herd and helped to solve computer problems by asking 
customers to turn their computers off and on again.}
%------------------------------------------------
\end{entrylist}

\clearpage

\smallheader{john}{smith}

%-------------------------------------------------------------------------------
%	AWARDS SECTION
%-------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2011}
{Postgraduate Scholarship}
{School of Business, The University of California}
{Awarded to the top student in their final year of a Bachelors degree.}
%------------------------------------------------
\end{entrylist}

%-------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%-------------------------------------------------------------------------------

\section{communication skills}

\begin{entrylist}
%------------------------------------------------
\entry
{2011}
{Oral Presentation}
{California Business Conference}
{Presented the research I conducted for my Masters of Commerce degree.}
%------------------------------------------------
\entry
{2010}
{Poster}
{Annual Business Conference, Oregon}
{As part of the course work for BUS320, I created a poster analyzing several 
local businesses and presented this at a conference.}
%------------------------------------------------
\end{entrylist}

%-------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-------------------------------------------------------------------------------

\section{publications}
\bibentry{Near a Raven -- A Critical Review of Poe's Works}{John 
Smith}{Sprinkler Publishing, New York, 2010}

\end{document}
