%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% K-CV -- Klenske Curriculum Vitae
% 
% Simplified Friggeri CV 
% by Edgar Klenske (ed.klenske@gmx.de)
% https://github.com/eklenske/CV
%
% Forked from:
% Jelmer Tiente 
% https://github.com/JelmerT/CV
%
% Based on original work by:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{k-cv} % Add 'print' as an option into the square
                       % bracket to remove colors from this template
                       % for printing
\usepackage[T1]{fontenc}
\newcommand\tab[1][1cm]{\hspace*{#1}}


\begin{document}
\header{Oliver James }{Hall}{PhD student in asteroseismology} % Your name and current job

%-------------------------------------------------------------------------------
%	SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{programming}
\bodyfont Python (advanced)
Unix, LaTeX, Git (intermediate)
R, SQL (basic)
\section{skills}
Stan
PyMC3
emcee 
Bayesian statistics
Hierarchical models
Asteroseismology
Software development \& publication (Python)
\section{languages}
English, Dutch (bilingual)
\section{contact}
School of Physics \& Astronomy
University of Birmingham
B15 2TT
Birmingham
United Kingdom
~
\href{mailto:ojh251@student.bham.ac.uk}{ojh251@bham.ac.uk}
\href{http://www.ojhall94.github.io}{ojhall94.github.io}
\href{http://www.github.com/ojhall94}{GitHub/ojhall94}
\href{http://www.twitter.com/asteronomer}{@asteronomer}
\href{http://www.orcid.com/0000-0002-0468-4775}{ORCID/}
\href{http://www.orcid.com/0000-0002-0468-4775}{0000-0002-0468-4775}
\end{aside}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{presentations}

\begin{entrylist}
%%------------------------------------------------
%\entry
%{2019 Nov.}
%{Seminar}
%{University of Exeter}
%{"..."}
%------------------------------------------------
\entry
{2019 Jul.}
{TASC5/KASC12}
{MIT, MA, USA}
{\textbf{Invited talk:} "Accessible Asteroseismology with Lightkurve"\\ \small{Poster: "Improving gyrochronology of field stars with asteroseismic age and rotation"}}
%------------------------------------------------
\entry
{2018 Dec.}
{Birmingham-Warwick Science Meet-Up}
{University of Warwick, UK}
{"Testing asteroseismology with \textit{Gaia} DR2: Hierarchical Models \& the Red Clump"}
%------------------------------------------------
\entry
{2018 Jul.}
{TASC4/KASC11}
{Aarhus University, Denmark}
{"Testing asteroseismology with \textit{Gaia} DR2: Luminosity of the Red Clump"}
%------------------------------------------------
\entry
{2017 Jul.}
{TASC3/KASC10}
{University of Birmingham, UK}
{\small{Poster: "Mixture Models applied to \emph{Kepler} backgrounds \& development for TESS"}}
%------------------------------------------------
\entry
{2017 Apr.}
{T'DA 2}
{Aarhus University, Denmark}
{"Estimating TESS backgrounds with mixture models -- Update"}
%------------------------------------------------
\entry
{2016 Nov.}
{T'DA 1}
{University of Birmingham, UK}
{"Estimating TESS backgrounds with mixture models"}
%------------------------------------------------
\end{entrylist}

\section{conferences \& workshops}

\begin{entrylist}
%------------------------------------------------
\entrythree
{2019 Oct.}
{T'DA 9 (\textbf{invited})}
{Institute for Astronomy, HI, USA}
%------------------------------------------------
\entrythree
{2019 Aug.}
{Astro Hack Week 2019}
{Kavli Institude for Cosmology, UK}
%------------------------------------------------
\entrythree
{2019 Jul.}
{TASC5/KASC12  (\textbf{invited})}
{MIT, MA, USA}
%------------------------------------------------
\entrythree
{2019 Jan.}
{T'DA 8}
{Aarhus University, Denmark}
%------------------------------------------------
\entrythree
{2018 Oct.}
{T'DA 5 (\textbf{invited})}
{Ohio State University, OH, USA}
%------------------------------------------------
\entrythree
{2018 Jul.}
{T'DA 4}
{Aarhus University, Denmark}
%------------------------------------------------
\entrythree
{2018 Jul.}
{TASC4/KASC11}
{Aarhus University, Denmark}
%------------------------------------------------
\entrythree
{2018 Jun.}
{The Wetton Workshop 2018}
{University of Oxford, UK}
%------------------------------------------------
\entrythree
{2017 Dec.}
{T'DA 3}
{KU Leuven, Belgium}
%------------------------------------------------
\entrythree
{2017 Jul.}
{TASC3/KASC10}
{University of Birmingham, UK}
%------------------------------------------------
\entrythree
{2017 Apr.}
{T'DA 2}
{Aarhus University, Denmark}
%------------------------------------------------
\entrythree
{2016 Nov.}
{Asteroseismology of stellar activity cycles}
{Observatoire de la C\^{o}te d'Azur, France}
%------------------------------------------------
\entrythree
{2016 Nov.}
{T'DA 1}
{University of Birmingham, UK}
%------------------------------------------------
\end{entrylist}


\section{research visits}
\begin{entrylist}
%------------------------------------------------
\entry
{2018 Oct.}
{Visit to the KeplerGO office [3 weeks]}
{NASA Ames Research Centre, CA, USA}
{Invited to build the \texttt{periodogram} module of \texttt{lightkurve}}
%------------------------------------------------
\entry
{2018 Jan.}
{Visit to SAC [1 week]}
{Aarhus University, Denmark}
{Invited to investigate \& build tools for background subtraction of TESS FFIs}
%----------------------------------------------
\end{entrylist}

\section{grants \& awards}

\begin{entrylist}
	%------------------------------------------------
	\entrythree
	{2019}
	{\textbf{\pounds 815} - Alumni Fund One-Off Grants}
	{The Ogden Trust, UK}
	%------------------------------------------------
	\entrythree
	{2018}
	{\textbf{\pounds 300} - IOP Research Student Conference Fund \emph{(declined)}}
	{Institute of Physics, UK}
	
	%------------------------------------------------
	\entrythree
	{2016}
	{\textbf{\pounds 3000} - Royal Society Partnership Grant}
	{The Royal Society, UK}
	%------------------------------------------------
	\entrythree
	{2015}
	{Teach Physics Oustanding Intern 2015 - shortlisted}
	{The Ogden Trust, UK}
	%------------------------------------------------
	
\end{entrylist}

\clearpage
\smallheader{oliver james  }{hall}


\section{education}

\begin{entrylist}
\centry
{2016 \to 2020}
{PhD {\normalfont in Physics \& Astronomy}}
{University of Birmingham, UK}
{Supervisor: Dr. Guy R. Davies\\
\textit{Thesis}: "Applied advanced statistics in asteroseismology"} 
%------------------------------------------------
%------------------------------------------------
\centry
{2012 \to 2016}
{M.Sci. {\normalfont Physics \& Astrophysics}}
{University of Birmingham, UK}
{Disseration supervisor: Prof. William J. Chaplin\\
1\textsuperscript{st} Class w. Honours}
%------------------------------------------------



%------------------------------------------------
\centry
{2006 \to 2012}
{Gymnasium}
{Gemeentelijk Gymnasium Hilversum, Netherlands}
{8.5/10 average across eleven subjects}
%------------------------------------------------
\end{entrylist}


\section{teaching and research}
\begin{entrylist}
%------------------------------------------------
\centry
{2019}
{Advanced HE - Associate Fellow (AFHEA)}
{Advanced HE}
{}
%------------------------------------------------
\centry
{2019}
{Access to Birmingham (A2B) supervisor}
{University of Birmingham}
{Support applicants from disenfranchised backgrounds through the A2B scheme.}
%------------------------------------------------
\centry
{2017 \to now}
{2\textsuperscript{nd} Year Laboratory Projects Demonstrator}
{University of Birmingham, UK}
{Taught students to build apparatus and understand their results. I marked their work and provided constructive feedback.}
%------------------------------------------------
\centry
{2016 \to now}
{3\textsuperscript{rd} Year Observatory Laboratory Supervisor}
{University of Birmingham, UK}
{Supervised students using an observatory. Helped students understand their results as well as the use of IRAF, Unix, and Python.}
%------------------------------------------------
\centry
{2015}
{Summer Undergraduate Reserach Experience (SURE)}
{University of Leicester, UK}
{Performed a six-week project using Python to program a robotic arm system for testing a prototype focal plane for the Cherenkov Telescope Array.}
%------------------------------------------------
\centry
{2015}
{Ogden Trust Teach Physics Intern}
{Bishop Challoner Catholic College, Birmingham, UK}
{Helped teach pupils throughout lessons, prepared and taught a lesson \& careers workshop.}
%------------------------------------------------
\end{entrylist}

\section{outreach \& engagement}
\begin{entrylist}
%------------------------------------------------
\centry
{2019 \to now}
{\emph{Author}, Astrobites Collaboration}
{}
{Write and edit monthly summaries of astronomy papers for an undergraduate level. \\ Committee member for \textbf{Advertising}, \textbf{Moderating}, \textbf{Hiring}, \textbf{Undergraduate Engagement}, and \textbf{Equality, Diversity \& Inclusion}}
%------------------------------------------------
\centry
{2019}
{\emph{Developer}, State of The Universe collaboration}
{Astro Hack Week 2019}
{Helped build and maintain an informative package for teachers and planetarium guides.}
%------------------------------------------------
\centry
{2018 \to 2019}
{\emph{Organiser}, 9\textsuperscript{th} BEAR Conference}
{University of Birmingham, UK}
{Organised local annual high performance computing conference.}
%------------------------------------------------
\centry
{2018 \to now}
{\emph{Demonstrator}, Applicant Visit Day}
{University of Birmingham, UK}
{Developed and taught laboratory sessions for undergraduate applicants.}
%------------------------------------------------
\centry
{2016 \to 2017}
{\emph{Partnered Researcher}, Royal Society Partnership Grant}
{}
{Developed and taught a series of lessons and lab activities engaging Year 9 pupils with exoplanet characterisation and asteroseismology.}
\end{entrylist}

\section{community services}
\begin{entrylist}
	%------------------------------------------------
	\centrythree
	{2018 \to now}
	{Member of the \texttt{lightkurve} collaboration}
	{NASA Ames Research Centre, CA, USA}
	%------------------------------------------------
	\centrythree
	{2016 \to now}
	{Member of the \emph{TESS Data for Asteroseismology} (T'DA) collaboration }
	{}
	%------------------------------------------------
	\centrythree
	{2016 \to now}
	{Member of the \emph{TESS Asteroseismic Science Consortium} (TASC)}
	{}
	%------------------------------------------------
	\centrythree
	{2017}
	{LOC member for TASC3/KASC11}
	{University of Birmingham, UK}
	%------------------------------------------------
\end{entrylist}


\clearpage
\smallheader{oliver james  }{hall}


\section{publications}
\bibentry{\textbf{Hall, O. J.}, Davies, G. R., Elsworth, Y. P. et al. [7 citations]}
{Testing asteroseismology with \textit{Gaia} DR2: Hierarchical models of the Red Clump}
{Monthly Notices of the Royal Astronomical Society, 2019}
{\texttt{doi:10.1093/mnras/stz1092, arXiv:1904.07919}}

\bibentry{{Khullar}, G., {Kholer}, S., {Konchady}, T. ... \textbf{{Hall}, O. J.} ... et al.}
{Astrobites as a Community-led Model for Education, Science Communication, and Accessibility in Astrophysics}
{arXiv e-prints, 2019}
{\texttt{arXiv:1907.09496}}

\bibentry{{Huber}, D., {Chaplin}, W. J., {Chontos}, A ... \textbf{{Hall}, O. J.} ... et al. [12 citations]}
{{A Hot Saturn Orbiting An Oscillating Late Subgiant Discovered by TESS}}
{arXiv e-prints, 2019}
{\texttt{doi:10.3847/1538-3881/ab1488, arXiv:1901.01643}}

\bibentry{{Bugnet}, L., {Garc{\'\i}a}, R. A., {Mathur}, S.,
         {Davies}, G. R., \textbf{{Hall}, O. J.}, {Lund}, M. N., {Rendle}, B. M. [1 citation]}
{FliPer$_{Class}$: In search of solar-like pulsators among TESS targets}
{arXiv e-prints, 2019}
{\texttt{doi:10.1051/0004-6361/201834780, arXiv:1902.09854}}

\bibentry{{Lightkurve Collaboration}, {Cardoso}, J. V. d. M., {Hedges}, C. ...       					\textbf{{Hall}, O. J.} ... et al. [5 citations]}
{Lightkurve: Kepler and TESS time series analysis in Python}
{Astrophysics Source Code Library, 2018}
{\texttt{ascl:1812.013}}

\bibentry{{Bugnet}, L., {Garc{\'\i}a}, R. A., {Davies}, G. R. ..
         \textbf{{Hall}, O. J.} ... et al. [9 citations]}
{FliPer: A global measure of power density to estimate surface gravities of main-sequence solar-like stars and red giants}
{Astronomy \& Astrophysics, 2018}
{\texttt{doi:0.1051/0004-6361/201833106, arXiv:1809.05105}}

\bibentry{{Khan}, S., \textbf{{Hall}, O. J.}, {Miglio}, A. et al. [7 citations]}
{The Red-giant Branch Bump Revisited: Constraints on Envelope Overshooting in a Wide Range of Masses and Metallicities}
{The Astrophysical Journal, 2018}
{\texttt{doi:10.3847/1538-4357/aabf90, arXiv:1804.06669}}

\bibentry{{Davies}, G. R., {Lund}, M. N. and {Miglio}, A. ... \textbf{Hall, O. J.} ... et al. [24 citations]}
{Using red clump stars to correct the \emph{Gaia} DR1 parallaxes}
{Astronomy \& Astrophysics, 2017}
{\texttt{doi:10.1051/0004-6361/201630066, arXiv:1701.02506}}

\end{document}
